manuscript_notes

### 2024-10-21 notes/manuscript_notes.Rmd
update ms.
respond to notes from Rich

@@

@@

@@

we use the terms hazard and EHA interchangeably. We should pick one, define it and then stick to it.

For example, the first line of the section "overview of hazard analysis" starts with "To apply event history analysis"

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

you say:

>Clearly, both weighting schemes prefer model M4.

@@

@@

@@

@@

@@

>>>>

-> Our custom functions are now located in the file custom_functions.R.
The functions are also listed in the supplementary material.

@@

-> The .bib file is generated automatically. I have solved the problem by adding the argument "append=F" to the function r_refs().

@@

-> ok.

@@

we use the terms hazard and EHA interchangeably. We should pick one, define it and then stick to it. 
For example, the first line of the section "overview of hazard analysis" starts with "To apply event history analysis"

-> I agree, but we are also discussing SAT analyses. I had a reviewer once who insisted that SAT is different from EHA. So we could talk about EHA/SAT analyses perhaps?

@@

-> all equations and formulas are moved to the supplementary material. Equations are numbered.

@@

-> Yes, the big code chunks are removed.

@@

-> still to do.

@@

-> I added the probability mass function P(t) for each condition.

@@

-> I added the following text:
These results go against the (often implicit) assumption that all observed responses are primed responses to the target stimulus. Instead, the distributional data show that early responses are triggered exclusively by the prime stimulus, while only later responses reflect primed responses to the target stimulus.

@@

-> I added the following text:
It is important to visually inspect the functions first for each participant, in order to identify possible cheaters (e.g., a flat conditional accuracy function at .5 indicates (s)he was only guessing), outlying individuals, and/or different groups with qualitatively different behavior.

When participants show qualitatively the same distributional patterns, on might consider to aggregate their data and make one plot (see Tutorial_1a.Rmd).

@@

-> I added the following text to the conclusion:
Statistically controlling for the passage of time during data analysis is thus equally important as experimental control during the design of an experiment, to better understand human behavior in experimental paradigms.

@@

-> I agree.

@@

-> Done.

@@

-> The example regression equations are moved to the supplementary material.

@@

-> I removed the code that lists priors. I kept the model code for M1, and the model formula for models M2 to M4.

@@

you say:
>Clearly, both weighting schemes prefer model M4.

@@

-> I added the output of the model_weights() functions to section 4.3.7.

@@

-> I added that table in Tutorials 2a and 2b.

@@

-> to do.

@@

-> I added the following text:
In the no-mask condition (column 1 in Figure 5), we observe a positive compatibility effect in the hazard and ca(t) functions, as congruent primes temporarily generate higher values for hazard and conditional accuracy compared to incongruent primes. However, when a (relevant, irrelevant, or lines) mask is present (columns 2-4), there is a negative compatibility effect in the hazard and conditional accuracy functions, as congruent primes temporarily generate *lower* values for hazard and conditional accuracy compared to incongruent primes.

@@

-> I simplified the text to this:
Second, because RT distributions may differ from one another in multiple ways, @townsendTruthConsequencesOrdinal1990 developed a dominance hierarchy of statistical differences between two arbitrary distributions A and B. For example, if h~A~(t) > h~B~(t) for all t, then both hazard functions are said to show a complete ordering. Townsend (1990) concluded that stronger conclusions can be drawn from data when comparing the hazard functions using EHA. For example, when mean A < mean B, the hazard functions might show a complete ordering (i.e., for all t), a partial ordering (e.g., only for t > 300 ms, or only for t < 500 ms), or they may cross each other one or more times.
